Invariant Representations for Noisy Speech Recognition

### 2016-11-30 poster.tex
Add gan picture

    \end{itemize}

@@

            \item Similar to the GAN objective, which forces the generation distribution be close to the data distribution,
            the \emph{gradient reverse method} makes domain distributions similar to each other.
        \end{itemize}

    \end{block}
\end{block}

>>>>

    \end{itemize}
    \begin{figure}
        \centering
        \includegraphics[width=0.5\linewidth]{gan.pdf}
    \end{figure}
\end{block}

@@

        \item Similar to the GAN objective, which forces the generation distribution be close to the data distribution,
        the \textcolor{dblue}{gradient reverse method} makes domain distributions similar to each other.
    \end{itemize}
